An elementary and constructive proof of Grothendieck's generic freeness lemma

### 2018-06-03 paper-generic-freeness.tex
Layout with shorter rows
typo

\usepackage{geometry}

@@

We remark that the proof takes a somewhat curious course: Our goal is to
verify~$1 = 0$, but as an intermediate step we verify that~$M$ is free, which
after the fact will be a trivial statement. The general proof in the next
section will have a similar style. This approach is reminiscient of
Richman's uses of trivial rings~\cite{richman:trivial-rings}.
\enlargethispage{8em}

\begin{figure}[H]
  \captionsetup{width=.9\linewidth}
  \begin{tikzpicture}[scale=0.9]
    \draw[step=1cm,gray,very thin] (0,0) grid (8,8);

@@

@@

Direct proofs sometimes generalize to new situations where the reduction techniques
employed in more abstract proofs cannot be applied. This is the case for
Grothendieck's generic freeness lemma, which allows for the following
generalization:

@@

It is hard to say with certainty that a given proof does not generalize to a
new situation; but we do not see how this could be the case with the proofs
cited in the introduction.

>>>>

@@

We remark that the proof takes a somewhat curious course: Our goal is to
verify~$1 = 0$, but as an intermediate step we verify that~$M$ is free, which
after the fact will be a trivial statement. The general proof in the next
section will have a similar style. This approach is reminiscient of
Richman's uses of trivial rings~\cite{richman:trivial-rings}.

@@

\begin{figure}[t]
  \captionsetup{width=.9\linewidth}
  \begin{tikzpicture}[scale=0.9]
    \draw[step=1cm,gray,very thin] (0,0) grid (8,8);

@@

Direct proofs sometimes generalize to new situations where the reduction techniques
employed by more abstract proofs cannot be applied. This is the case for
Grothendieck's generic freeness lemma, which allows for the following
generalization:

@@

It is hard to say with certainty that a given proof does not generalize to a
new situation; but we do not see how this could be the case for the proofs
cited in the introduction.
